Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-07 paper/paper.tex
Add first pass at conclusion

Recent trends have shown a proliferation of databases termed ``NoSQL'' which frequently eschew traditional database concepts such as referential integrity and ACID transactions for the sake of performance.
However, applications using these databases still have a need to perform complex queries.
Especially in the case of analytical queries, this may force the application designer to implement constructs such as joins at the application level.
This requires a significant amount of data transfer between nodes.
Given that it is common for data to be held in memory for performance reasons, the bottleneck for this data transfer is pushed up to the network layer.

@@

>>>>

Recent trends have shown a proliferation of databases termed ``NoSQL'' which frequently eschew traditional database concepts such as referential integrity, ACID transactions, and high-level query languages for the sake of performance.
However, applications using these databases still have a need to perform complex queries.
Especially in the case of analytical queries, this may force the application designer to implement constructs such as joins at the application level.
This requires a significant amount of data transfer between nodes.
Given that it is common for data to be held in memory for performance reasons, the bottleneck for this data transfer is pushed up to the network layer.

@@

In this work, we examined opportunties to apply software-defined network techniques to provide more efficient query processing over NoSQL databases.
We demonstrated a simple technique using smart network scheduling to improve the performance of distributed joins.
Our technique provides a significant performance improvement over uninformed switching techniques.

We also presented several opportunties to further exploit of software-defined network techniques to improve query processing.
As software-defined networking becomes increasingly common in datacentres, we feel similar techniques will become increasingly prevalent.
Little work has been done to exploit software-defined networking in the context of NoSQL databases and distributed data management.
